---
title: "Climate Change Conversations Study 2"
author: "Ovidia Stanoi"
date: "08/24/2026"
output:
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
    theme: united
    highlight: tango
    df_print: paged
    toc_float: true
    css: styles.css
    tabset: true
  pdf_document: default
---

```{r setup, include=FALSE,warning=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# Clear global environment
remove(list=ls())

# Open libraries
library("tidyverse")
library("knitr")
library("kableExtra")
library("reactable")
library("patchwork")

# Set global ggplot theme
plot_aes = theme_minimal() +
theme(legend.text = element_text(size = 8),
        text = element_text(size = 16),
        axis.text = element_text(color = "black"),
        axis.ticks.y = element_blank(),
        legend.position = "none",
        plot.title = element_text(hjust = 0.5), 
        plot.title.position = "plot",
        panel.spacing.x = unit(1.5, "lines"), 
        strip.text = element_text(size = 12),
        plot.margin = margin(t = 5, r = 5, b = 5, l = 5))

# Define colors
palette <- c("#67C5CA",  "#F18448", "#3B506E", "#F5964E", 
             "#262D63", "#FCE7EF", "#FBEFD6") 

# Define path where data are stored
filedir <- "~/Library/CloudStorage/Dropbox/Psychology_Projects/Climate Change Conversations"

# Load the dataset containing the conversation benefits generated by participants
benefits <- read.csv(sprintf("%s/Data/Conversation Beliefs Elicitation Survey/Clean/Convo_benefits_themes.csv",
                             filedir))  %>%
  mutate(conversation_partner = factor(conversation_partner, levels = c("Important Others", 
                                        "Most Comfortable", 
                                        "Least Comfortable"))) %>%
  filter(!(theme == "" | is.na(theme) | theme == "Other"))

# Load the dataset containing the conversation disadvantages generated by participants
disadvantages <- read.csv(sprintf("%s/Data/Conversation Beliefs Elicitation Survey/Clean/Convo_disadvantages_themes.csv", 
                                  filedir)) %>%
  mutate(conversation_partner = factor(conversation_partner, levels = c("Important Others", 
                                        "Most Comfortable", 
                                        "Least Comfortable"))) %>%
  filter(!(theme == "" | is.na(theme) | theme == "Other"))

# Load the dataset containing the conversation facilitators generated by participants
easy <- read.csv(sprintf("%s/Data/Conversation Beliefs Elicitation Survey/Clean/Convo_control_factors_easy_themes.csv", 
                                  filedir)) %>%
  mutate(conversation_partner = factor(conversation_partner, levels = c("Important Others", 
                                        "Most Comfortable", 
                                        "Least Comfortable"))) %>%
  filter(!(theme == "" | is.na(theme) | theme == "Other"))

# Load the dataset containing the conversation barriers generated by participants
difficult <- read.csv(sprintf("%s/Data/Conversation Beliefs Elicitation Survey/Clean/Convo_control_factors_difficult_themes.csv", 
                                  filedir)) %>%
  mutate(conversation_partner = factor(conversation_partner, levels = c("Important Others", 
                                        "Most Comfortable", 
                                        "Least Comfortable"))) %>%
  filter(!(theme == "" | is.na(theme) | theme == "Other"))

# Load the dataset containing the conversation goals generated by participants
goals_self <- read.csv(sprintf("%s/Data/Conversation Beliefs Elicitation Survey/Clean/Convo_goals_self_themes.csv",
                               filedir)) %>%
  mutate(conversation_partner = factor(conversation_partner, levels = c("Most Comfortable", 
                                        "Least Comfortable"))) %>%
  filter(!(theme == "" | is.na(theme) | theme == "Other"))

# Load the dataset containing the perceived goals of different conversation partners generated by participants
goals_other <- read.csv(sprintf("%s/Data/Conversation Beliefs Elicitation Survey/Clean/Convo_goals_partner_themes.csv",
                               filedir)) %>%
  mutate(conversation_partner = factor(conversation_partner, levels = c( "Most Comfortable", 
                                        "Least Comfortable"))) %>%
  filter(!(theme == "" | is.na(theme) | theme == "Other"))
```

<br>

We recruited a sample of 202 participants on Prolific to complete a 20-min elicitation survey about their climate change conversations. Participants were asked to reflect on the following behavior: **“openly sharing their thoughts, feelings, and opinions about climate change in conversations”**. Half of the sample were asked about this behavior with **“the people who are important to them”** (general group). The other half was asked about it in relation to two people: one with whom they would feel **most comfortable** and one with whom they would feel **least comfortable** talking (ego group). For each social target, participants gave open-ended responses about what they saw as the **benefits** and the **disadvantages** of sharing their thoughts about climate change with them as well as what factors would make it **easier** or **more difficult** for them to talk in the future. Participants in the ego group were also asked to list any **goals** they themselves would hope to achieve in a hypothetical conversation with these different social targets and the goals they believe the other person would hope to achieve. We used a large language model (ChatGPT-4) to identify high-level themes in the participants’ open-ended answers in an unsupervised manner. Answers were subsequently manually coded according to these themes by the research team. We present below the results. 

<br>

# Conversation Benefits {.tabset}

## Main Themes {.unnumbered}

<br> 

Participants associated climate change conversations with a variety of benefits, which broadly clustered into four categories: **raising awareness** about the dangers of climate change, **influencing change** and contributing to mitigating efforts, feeling emotionally **connected**, and **sharing perspective**. We present below the percentages of the answers classified in each theme for each of the three possible conversation partners: important others broadly defined, individuals with whom participants would feel the most comfortable talking, and individuals with whom they would feel the least comfortable talking. 

<br> 

```{r}
# Count most common benefits within each theme
topic_counts <- benefits %>%
  group_by(conversation_partner) %>%
  count(theme) %>%
  mutate(percent = round(n / sum(n),2)) %>%
  filter(!(theme == "")) %>%
  arrange(conversation_partner, - percent)
kable(topic_counts)

# Plot results
p_benefits <- ggplot(topic_counts, aes(x = reorder(theme, percent), y = percent)) +
  geom_bar(stat = "identity", aes(fill = conversation_partner), 
           color = "black") +
  coord_flip() +
  facet_wrap(~ conversation_partner) +
  labs(x = NULL,
       y = "Percentage", 
       title = "Perceived Conversation Benefits") +
  scale_fill_manual(values = palette[1:3]) +
  scale_y_continuous(breaks = seq(0, .4, by = .2),
                     labels = scales::percent_format()) +
  plot_aes

# Save plot
{ragg::agg_tiff(sprintf("%s/Figures/study2_convo_benefits.tiff", 
                       filedir),
              width = 1920, height = 1080, 
              units = "px", res = 300)
print(p_benefits)
invisible(dev.off())}

# See plot
p_benefits
```

##  Text {.unnumbered}

<br> 

All responses are presented below with their assigned theme. 

<br> 

```{r, echo = F, messages = F, warnings = F}
benefits %>%
  reactable(striped = TRUE,
            filterable = TRUE)
```

# Conversation Disadvantages {.tabset}

## Main Themes {.unnumbered}

<br> 

Perceived disadvantages of climate change conversations clustered around four themes: **disagreement** or conflict, **emotional discomfort**, being **dismissed** or judged, and the need to invest additional time and **resources**. See below the percentages of the answers classified in each theme for each of the three possible conversation partners: important others broadly defined, individuals with whom participants would feel the most comfortable talking, and individuals with whom they would feel the least comfortable talking. 

<br> 

```{r}
# Count most common disadvantages within each theme
topic_counts <- disadvantages %>%
  group_by(conversation_partner) %>%
  count(theme) %>%
  mutate(percent = round(n / sum(n),2)) %>%
  filter(!(theme == "")) %>%
  arrange(conversation_partner, - percent)
kable(topic_counts)

# Plot results
p_disadvantages <- ggplot(topic_counts, aes(x = reorder(theme, percent), y = percent)) +
  geom_bar(stat = "identity", aes(fill = conversation_partner), 
           color = "black") +
  coord_flip() +
  facet_wrap(~ conversation_partner) +
  labs(x = NULL,
       y = "Percentage", 
       title = "Perceived Conversation Disadvantages") +
  scale_fill_manual(values = palette[1:3]) +
  scale_y_continuous(breaks = seq(0, .4, by = .2),
                     labels = scales::percent_format()) +
  plot_aes

# Save plot
{ragg::agg_tiff(sprintf("%s/Figures/study2_convo_disadvantages.tiff", 
                       filedir),
              width = 1920, height = 1080, 
              units = "px", res = 300)
print(p_disadvantages)
invisible(dev.off())}

# See plot
p_disadvantages
```

##  Text {.unnumbered}

<br> 

All responses are presented below with their assigned theme. 

<br> 

```{r, echo = F, messages = F, warnings = F}
disadvantages %>%
  reactable(striped = TRUE,
            filterable = TRUE)
```

# Conversation Facilitators {.tabset}

## Main Themes {.unnumbered}

<br> 

Participants identified four clusters of factors that would make it easier to talk about climate change in the future: if they knew that their **conversation partner shared and respected their perspective**, if they had **access to reliable information** and felt confident in their knowledge, if they had more time and **resources**, and finally if they were talking to someone to whom they felt **close**. See below the percentages of the answers associated with each theme for each of the three possible conversation partners: important others broadly defined, individuals with whom participants would feel the most comfortable talking, and individuals with whom they would feel the least comfortable talking. 

<br> 

```{r}
# Count most common facilitators within each theme
topic_counts <- easy %>%
  group_by(conversation_partner) %>%
  count(theme) %>%
  mutate(percent = round(n / sum(n),2)) %>%
  filter(!(theme == "")) %>%
  arrange(conversation_partner, - percent)
kable(topic_counts)

# Plot results
p_facilitators <- ggplot(topic_counts, aes(x = reorder(theme, percent), y = percent)) +
  geom_bar(stat = "identity", aes(fill = conversation_partner), 
           color = "black") +
  coord_flip() +
  facet_wrap(~ conversation_partner) +
  labs(x = NULL,
       y = "Percentage", 
       title = "Perceived Conversation Facilitators") +
  scale_fill_manual(values = palette[1:3]) +
  scale_y_continuous(breaks = seq(0, .5, by = .2),
                     labels = scales::percent_format()) +
  plot_aes

# Save plot
{ragg::agg_tiff(sprintf("%s/Figures/study2_convo_facilitators.tiff", 
                       filedir),
              width = 1920, height = 1080, 
              units = "px", res = 300)
print(p_facilitators)
invisible(dev.off())}

# See plot
p_facilitators
```

##  Text {.unnumbered}

<br> 

All responses are presented below with their assigned theme. 

<br> 

```{r, echo = F, messages = F, warnings = F}
easy %>%
  reactable(striped = TRUE,
            filterable = TRUE)
```

# Conversation Barriers {.tabset}

## Main Themes {.unnumbered}

<br> 

Barriers to conversations clustered into seven themes: **disagreement** with someone with opposing views, interacting with a **dismissive** conversation partner, **negative emotions**, **lack of information** and confidence in one’s communication skills, lack of time and **resources**, facing **external events** or politics, **social norms** or roles that do not sanction climate conversations. See below the percentages of the answers associated with each theme for each of the three possible conversation partners: important others broadly defined, individuals with whom participants would feel the most comfortable talking, and individuals with whom they would feel the least comfortable talking. 

<br> 

```{r}
# Count most common barriers within each theme
topic_counts <- difficult %>%
  group_by(conversation_partner) %>%
  count(theme) %>%
  mutate(percent = round(n / sum(n),2)) %>%
  filter(!(theme == "")) %>%
  arrange(conversation_partner, - percent)
kable(topic_counts)

# Plot results
p_barriers <- ggplot(topic_counts, aes(x = reorder(theme, percent), y = percent)) +
  geom_bar(stat = "identity", aes(fill = conversation_partner), 
           color = "black") +
  coord_flip() +
  facet_wrap(~ conversation_partner) +
  labs(x = NULL,
       y = "Percentage", 
       title = "Perceived Conversation Barriers") +
  scale_fill_manual(values = palette[1:3]) +
  scale_y_continuous(breaks = seq(0, .3, by = .2),
                     labels = scales::percent_format()) +
  plot_aes

# Save plot
{ragg::agg_tiff(sprintf("%s/Figures/study2_convo_barriers.tiff", 
                       filedir),
              width = 1920, height = 1080, 
              units = "px", res = 300)
print(p_barriers)
invisible(dev.off())}

# See plot
p_barriers
```

##  Text {.unnumbered}

<br> 

All responses are presented below with their assigned theme. 

<br> 

```{r, echo = F, messages = F, warnings = F}
difficult %>%
  reactable(striped = TRUE,
            filterable = TRUE)
```

# Personal Conversation Goals {.tabset}

## Main Themes {.unnumbered}

<br> 

Participants’ personal goals for climate conversations across groups clustered into six themes: **empowering action**, **sharing information and persuading**, **gaining mutual understanding**, **feeling less negative or more positive**, **feeling closer to the other person**, and **feeling heard**. See below the percentages of the answers associated with each theme for each of the three possible conversation partners: important others broadly defined, individuals with whom participants would feel the most comfortable talking, and individuals with whom they would feel the least comfortable talking. 

<br> 

```{r}
# Count most common goals within each theme
topic_counts <- goals_self %>%
  group_by(conversation_partner) %>%
  count(theme) %>%
  mutate(percent = round(n / sum(n),2)) %>%
  filter(!(theme == "")) %>%
  arrange(conversation_partner, - percent)
kable(topic_counts)

# Plot results
p_goals_self <- ggplot(topic_counts, aes(x = reorder(theme, percent), y = percent)) +
  geom_bar(stat = "identity", aes(fill = conversation_partner), 
           color = "black") +
  coord_flip() +
  facet_wrap(~ conversation_partner) +
  labs(x = NULL,
       y = "Percentage", 
       title = "Personal Goals") +
  scale_fill_manual(values = palette[2:3]) +
  scale_y_continuous(breaks = seq(0, .4, by = .2),
                     labels = scales::percent_format()) +
  plot_aes

# Save plot
{ragg::agg_tiff(sprintf("%s/Figures/study2_convo_goals_self.tiff", 
                       filedir),
              width = 1920, height = 1080, 
              units = "px", res = 300)
print(p_goals_self)
invisible(dev.off())}

# See plot
p_goals_self
```

##  Text {.unnumbered}

<br> 

All responses are presented below with their assigned theme. 

<br> 

```{r, echo = F, messages = F, warnings = F}
goals_self %>%
  reactable(striped = TRUE,
            filterable = TRUE)
```

# Perceived Conversation Goals of Different Conversation Partners {.tabset}

## Main Themes {.unnumbered}

<br> 

Participants’ perceptions of their conversation partners’ goals clustered into nine categories, mirroring their own goals with three additions: **protecting current beliefs**, **listening and validating**, and **suppressing conversation**. See below the percentages of the answers associated with each theme for each of the three possible conversation partners: important others broadly defined, individuals with whom participants would feel the most comfortable talking, and individuals with whom they would feel the least comfortable talking. 

<br> 

```{r}
# Count most common goals within each theme
topic_counts <- goals_other %>%
  group_by(conversation_partner) %>%
  count(theme) %>%
  mutate(percent = round(n / sum(n),2)) %>%
  filter(!(theme == "")) %>%
  arrange(conversation_partner, - percent)
kable(topic_counts)

# Plot results
p_goals_other <- ggplot(topic_counts, aes(x = reorder(theme, percent), y = percent)) +
  geom_bar(stat = "identity", aes(fill = conversation_partner), 
           color = "black") +
  coord_flip() +
  facet_wrap(~ conversation_partner) +
  labs(x = NULL,
       y = "Percentage", 
       title = "Perceived Goals of Conversation Partner") +
  scale_fill_manual(values = palette[2:3]) +
  scale_y_continuous(breaks = seq(0, .4, by = .2),
                     labels = scales::percent_format()) +
  plot_aes

# Save plot
{ragg::agg_tiff(sprintf("%s/Figures/study2_convo_goals_other.tiff", 
                       filedir),
              width = 1920, height = 1080, 
              units = "px", res = 300)
print(p_goals_other)
invisible(dev.off())}

# See plot
p_goals_other
```

##  Text {.unnumbered}

<br> 

All responses are presented below with their assigned theme. 

<br> 

```{r, echo = F, messages = F, warnings = F}
goals_other %>%
  reactable(striped = TRUE,
            filterable = TRUE)
```

# Manuscript Plots {.tabset}

## Figure 3 {.unnumbered}

<br>

Below see the script used to generate Figure 3 in the main manuscript. 

<br>

```{r}
tiff(sprintf("%s/Figures/Figure 3. Study 2 Results Beliefs.tiff", filedir),
     width = 14, height = 8, units = "in", res = 300, compression = "lzw")

wrap_plots(p_benefits, p_disadvantages, p_facilitators, p_barriers) +
  plot_layout(axis_titles = "collect", ncol = 2) +
  plot_annotation(tag_levels = 'A', tag_suffix = '.') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))

invisible(dev.off())
```

## Figure 4 {.unnumbered}

<br>

Below see the script used to generate Figure 4 in the main manuscript. 

<br>

```{r}
tiff(sprintf("%s/Figures/Figure 4. Study 2 Results Goals.tiff", filedir),
     width = 14, height = 6, units = "in", res = 300, compression = "lzw")

wrap_plots(p_goals_self, p_goals_other) +
  plot_layout(axis_titles = "collect", ncol = 2) +
  plot_annotation(tag_levels = 'A', tag_suffix = '.') & 
  theme(plot.tag = element_text(size = 20, face = "bold"),
        text = element_text(size = 18))

invisible(dev.off())
```

